Universal Anonymous Signatures

### 2022-04-05 prism-backend/research/gsac/preliminaries.tex
Merged GSAC and UAS into uas.tex paper. Defining concrete instantiation of GSAC.
Seemingly stable model anc concrete instantiation for GSAC.
Working on generic construction of GSAC.

\subsection{Building Blocks}
\label{ssec:bblocks}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "gsac"
%%% End:

>>>>

\subsection{Cryptographic Building Blocks}
\label{ssec:cryptobblocks}

\todo{NIZKs.}

\subsubsection{Notation}
\label{ssec:notation}

\todo{Attribute space. Used in generic construction of GSAC for now. Define it
  to be the set of bitstrings of some length.}

\todo{\Attrs and \DAttrs (in \secref{ssec:construction-gsac}, they are treated
  as indices, but I think that's not the case elsewhere).}

\todo{In \secref{ssec:construction-gsac}, we assume that all messages and
  attributes can be encoded as elements in $\ZZ^*_p$.}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "uas"
%%% End:
